Component response rate variation underlies the stability of complex systems

### 2020-03-11 notebook/SI.Rmd
Rearrange the SI to better match the main text

- [Stability across increasing $S$](#IncrS) 
- [Stability given targeted manipulation of $\gamma$ (genetic algorithm)](#ga)
- [Stability of ecological networks](#ecological) 
    - [Competitor networks](#competition) 
    - [Mutualist networks](#mutualism) 
    - [Predator-prey networks](#pred-prey) 
- [Sensitivity of connectance (C) values](#connectance)
    - [C = 0.3](#connect3)
    - [C = 0.5](#connect5)
    - [C = 0.7](#connect7)
    - [C = 0.9](#connect9)
- [Large networks of $C = 0.05$ across $S$ and $\sigma$](#sigma)  
    - [$\sigma$ = 0.3](#sigma3)
    - [$\sigma$ = 0.4](#sigma4)
    - [$\sigma$ = 0.5](#sigma5)
    - [$\sigma$ = 0.6](#sigma6)
- [Sensitivity of distribution of $\gamma$](#gam_dist)
- [Feasibility of complex systems](#Feasibility)
- [Consistency with Gibbs et al. (2018)](#Gibbs)
- [Effects of matrix correlations](#rhos)

>>>>

- [Stability across increasing $S$](#IncrS) 
- [Stability of ecological networks](#ecological) 
    - [Competitor networks](#competition) 
    - [Mutualist networks](#mutualism) 
    - [Predator-prey networks](#pred-prey) 
- [Sensitivity of connectance (C) values](#connectance)
    - [C = 0.3](#connect3)
    - [C = 0.5](#connect5)
    - [C = 0.7](#connect7)
    - [C = 0.9](#connect9)
- [Large networks of $C = 0.05$ across $S$ and $\sigma$](#sigma)  
    - [$\sigma$ = 0.3](#sigma3)
    - [$\sigma$ = 0.4](#sigma4)
    - [$\sigma$ = 0.5](#sigma5)
    - [$\sigma$ = 0.6](#sigma6)
- [Sensitivity of distribution of $\gamma$](#gam_dist)
- [Feasibility of complex systems](#Feasibility)
- [Stability given targeted manipulation of $\gamma$ (genetic algorithm)](#ga)
- [Consistency with Gibbs et al. (2018)](#Gibbs)
- [Effects of matrix correlations](#rhos)

### 2020-03-11 notebook/SI.tex
Rearrange the SI to better match the main text

\hypertarget{supplemental-information-table-of-contents}{%
\section{Supplemental Information table of
contents}\label{supplemental-information-table-of-contents}}

\begin{itemize}
\tightlist
\item
  \protect\hyperlink{IncrS}{Stability across increasing \(S\)}
\item
  \protect\hyperlink{ga}{Stability given targeted manipulation of
  \(\gamma\) (genetic algorithm)}
\item
  \protect\hyperlink{ecological}{Stability of ecological networks}

@@

  \begin{itemize}
  \tightlist
  \item
    \protect\hyperlink{sigma3}{\(\sigma\) = 0.3}
  \item
    \protect\hyperlink{sigma4}{\(\sigma\) = 0.4}
  \item
    \protect\hyperlink{sigma5}{\(\sigma\) = 0.5}
  \item
    \protect\hyperlink{sigma6}{\(\sigma\) = 0.6}
  \end{itemize}
\item
  \protect\hyperlink{gam_dist}{Sensitivity of distribution of
  \(\gamma\)}
\item
  \protect\hyperlink{Feasibility}{Feasibility of complex systems}
\item
  \protect\hyperlink{Gibbs}{Consistency with Gibbs et al. (2018)}
\item
  \protect\hyperlink{rhos}{Effects of matrix correlations}
\end{itemize}

\hypertarget{IncrS}{%
\section{\texorpdfstring{Stability across increasing
\(S\)}{Stability across increasing S}}\label{IncrS}}

@@

\hypertarget{ga}{%
\section{\texorpdfstring{Stability given targeted manipulation of
\(\gamma\) (genetic
algorithm)}{Stability given targeted manipulation of \textbackslash{}gamma (genetic algorithm)}}\label{ga}}

\includegraphics{SI_files/figure-latex/unnamed-chunk-6-1.pdf}

\includegraphics{SI_files/figure-latex/unnamed-chunk-8-1.pdf}

\hypertarget{ecological}{%
\section{Stability of ecological networks}\label{ecological}}

@@

\hypertarget{connectance}{%
\section{Sensitivity of connectance (C) values}\label{connectance}}

@@

\hypertarget{sigma}{%
\section{\texorpdfstring{Sensitivity of interaction strength
(\(\sigma\))
values}{Sensitivity of interaction strength (\textbackslash{}sigma) values}}\label{sigma}}

@@

\hypertarget{gam_dist}{%
\section{\texorpdfstring{Sensitivity of distribution of
\(\gamma\)}{Sensitivity of distribution of \textbackslash{}gamma}}\label{gam_dist}}

@@

@@

\hypertarget{Feasibility}{%
\section{Feasibility of complex systems}\label{Feasibility}}

@@

\hypertarget{Gibbs}{%
\section{Consistency with Gibbs et al. (2018)}\label{Gibbs}}

@@

\hypertarget{effects-of-matrix-correlations}{%
\section{Effects of matrix
correlations}\label{effects-of-matrix-correlations}}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-May1972}{}%
1. May, R. M. Will a large complex system be stable? \emph{Nature}
\textbf{238,} 413--414 (1972).

\leavevmode\hypertarget{ref-Allesina2012}{}%
2. Allesina, S. \& Tang, S. Stability criteria for complex ecosystems.
\emph{Nature} \textbf{483,} 205--208 (2012).

\leavevmode\hypertarget{ref-Allesina2015}{}%
3. Allesina, S. \emph{et al.} Predicting the stability of large
structured food webs. \emph{Nature Communications} \textbf{6,} 7842
(2015).

\leavevmode\hypertarget{ref-Servan2018}{}%
4. Serván, C. A., Capitán, J. A., Grilli, J., Morrison, K. E. \&
Allesina, S. Coexistence of many species in random ecosystems.
\emph{Nature Ecology and Evolution} \textbf{2,} 1237--1242 (2018).

\leavevmode\hypertarget{ref-Gibbs2017}{}%
5. Gibbs, T., Grilli, J., Rogers, T. \& Allesina, S. The effect of
population abundances on the stability of large random ecosystems.
\emph{Physical Review E - Statistical, Nonlinear, and Soft Matter
Physics} \textbf{98,} 022410 (2018).

>>>>

\section{Supplemental Information table of
contents}\label{supplemental-information-table-of-contents}

\begin{itemize}
\tightlist
\item
  \protect\hyperlink{IncrS}{Stability across increasing \(S\)}
\item
  \protect\hyperlink{ecological}{Stability of ecological networks}

@@

  \begin{itemize}
  \tightlist
  \item
    \protect\hyperlink{sigma3}{\(\sigma\) = 0.3}
  \item
    \protect\hyperlink{sigma4}{\(\sigma\) = 0.4}
  \item
    \protect\hyperlink{sigma5}{\(\sigma\) = 0.5}
  \item
    \protect\hyperlink{sigma6}{\(\sigma\) = 0.6}
  \end{itemize}
\item
  \protect\hyperlink{gam_dist}{Sensitivity of distribution of
  \(\gamma\)}
\item
  \protect\hyperlink{Feasibility}{Feasibility of complex systems}
\item
  \protect\hyperlink{ga}{Stability given targeted manipulation of
  \(\gamma\) (genetic algorithm)}
\item
  \protect\hyperlink{Gibbs}{Consistency with Gibbs et al. (2018)}
\item
  \protect\hyperlink{rhos}{Effects of matrix correlations}
\end{itemize}

\hypertarget{IncrS}{\section{\texorpdfstring{Stability across increasing
\(S\)}{Stability across increasing S}}\label{IncrS}}

@@

\hypertarget{ecological}{\section{Stability of ecological
networks}\label{ecological}}

@@

\hypertarget{connectance}{\section{Sensitivity of connectance (C)
values}\label{connectance}}

@@

\hypertarget{sigma}{\section{\texorpdfstring{Sensitivity of interaction
strength (\(\sigma\))
values}{Sensitivity of interaction strength (\textbackslash{}sigma) values}}\label{sigma}}

@@

\hypertarget{gam_dist}{\section{\texorpdfstring{Sensitivity of
distribution of
\(\gamma\)}{Sensitivity of distribution of \textbackslash{}gamma}}\label{gam_dist}}

@@

\includegraphics{SI_files/figure-latex/unnamed-chunk-21-1.pdf}

@@

\hypertarget{Feasibility}{\section{Feasibility of complex
systems}\label{Feasibility}}

@@

\hypertarget{ga}{\section{\texorpdfstring{Stability given targeted
manipulation of \(\gamma\) (genetic
algorithm)}{Stability given targeted manipulation of \textbackslash{}gamma (genetic algorithm)}}\label{ga}}

\includegraphics{SI_files/figure-latex/unnamed-chunk-26-1.pdf}

\hypertarget{Gibbs}{\section{Consistency with Gibbs et al.
(2018)}\label{Gibbs}}

@@

\section{Effects of matrix
correlations}\label{effects-of-matrix-correlations}

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-May1972}{}
1. May, R. M. Will a large complex system be stable? \emph{Nature}
\textbf{238,} 413--414 (1972).

\hypertarget{ref-Allesina2012}{}
2. Allesina, S. \& Tang, S. Stability criteria for complex ecosystems.
\emph{Nature} \textbf{483,} 205--208 (2012).

\hypertarget{ref-Allesina2015}{}
3. Allesina, S. \emph{et al.} Predicting the stability of large
structured food webs. \emph{Nature Communications} \textbf{6,} 7842
(2015).

\hypertarget{ref-Servan2018}{}
4. Serván, C. A., Capitán, J. A., Grilli, J., Morrison, K. E. \&
Allesina, S. Coexistence of many species in random ecosystems.
\emph{Nature Ecology and Evolution} \textbf{2,} 1237--1242 (2018).

\hypertarget{ref-Gibbs2017}{}
5. Gibbs, T., Grilli, J., Rogers, T. \& Allesina, S. The effect of
population abundances on the stability of large random ecosystems.
\emph{Physical Review E - Statistical, Nonlinear, and Soft Matter
Physics} \textbf{98,} 022410 (2018).
